Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-14 paper_quarto.qmd
punctuation remove

## 1. Research Question

Natural History by Pliny the Elder is considered the very first encyclopedia in modern history. It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time. As it is a text containing rich research potentials,

## 2. Corpus Description

@@

## 3. Keyword Analysis on India-related texts

## 4. Collocation Analysis on "India" in the whole corpus

@@

## 5. Conclusion

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

# 1. Research Question

Natural History by Pliny the Elder is considered the very first encyclopedia in modern history. It not only showcased the actual merchant exchange of the Roman Empire, but also manifested the spatial imagination of Pliny the Elder and the referenced scholarships of that time.

# 2. Corpus Description

As there is a digitized and name entities annotated full text available on [ToposText project](https://topostext.org/work/148 "Check Natural History on ToposText"), I scraped the full text and exported them in .txt as a corpus, and also exported those with geographical location annotations, which considered as geographically related texts as a sub corpus.

(statistics)

# 3. Data Preparation

```{r}
#| label: chunk
#| output: false
#| warning: false
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')

corpus_folder <- here("NH_wholetext")
fnames_wholetext <- get_fnames(corpus_folder) %>% 
  keep_re("[.]txt")

print(fnames_wholetext, 10, hide_path = corpus_folder)

corpus_folder <-  here("NH_geotext_india")
fnames_indiatext <- get_fnames(corpus_folder) %>% 
  keep_re("[.]txt")

print(fnames_indiatext, 10, hide_path = corpus_folder)
```

# 4. Keyword Analysis on India-related texts

```{r}
# build frequency list for target corpus
flist_target <- fnames_indiatext %>%
  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
           file_encoding     = "windows-1252") %>%
  print()
# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
           file_encoding     = "windows-1252") %>%
  print()
```

```{r}
flist_target %>% 
  as_tibble() %>% 
  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
  kable_minimal(full_width = FALSE) %>% 
  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
  scroll_box(height = "400px")
```

# 5. Collocation Analysis on "India" in the whole corpus

@@

# 6. Conclusion

@@
